---
title: "Week 7 Assignment"
author: "Jiaxin Zheng"
date: "2024-10-19"
output:
  html_document: default
  pdf_document: default
---

```{r}
#create the data frame
data <- data.frame(
  Category = c("Electronics", "Electronics", "Electronics", "Electronics", 
               "Home Appliances", "Home Appliances", "Home Appliances", "Home Appliances", 
               "Clothing", "Clothing", "Clothing", "Clothing", 
               "Books", "Books", "Books", "Books", 
               "Sports Equipment", "Sports Equipment"),
  Item_Name = c("Smartphone", "Smartphone", "Laptop", "Laptop", 
                "Refrigerator", "Refrigerator", "Washing Machine", "Washing Machine", 
                "T-Shirt", "T-Shirt", "T-Shirt", "Jeans", 
                "Fiction Novel", "Fiction Novel", "Non-Fiction Guide", "Non-Fiction Guide", 
                "Basketball", "Tennis Racket"),
  Item_ID = c(101, 101, 102, 102, 201, 201, 202, 202, 301, 301, 301, 302, 401, 401, 402, 402, 501, 502),
  Brand = c("TechBrand", "TechBrand", "CompuBrand", "CompuBrand", 
            "HomeCool", "HomeCool", "CleanTech", "CleanTech", 
            "FashionCo", "FashionCo", "FashionCo", "DenimWorks", 
            "-", "-", "-", "-", 
            "SportsGear", "RacketPro"),
  Price = c(699.99, 699.99, 1099.99, 1099.99, 899.99, 899.99, 499.99, 499.99, 
            19.99, 19.99, 19.99, 49.99, 14.99, 14.99, 24.99, 24.99, 29.99, 89.99),
  Variation_ID = c("101-A", "101-B", "102-A", "102-B", 
                   "201-A", "201-B", "202-A", "202-B", 
                   "301-A", "301-B", "301-C", "302-A", 
                   "401-A", "401-B", "402-A", "402-B", 
                   "501-A", "502-A"),
  Variation_Details = c("Color: Black, Storage: 64GB", "Color: White, Storage: 128GB", 
                        "Color: Silver, Storage: 256GB", "Color: Space Gray, Storage: 512GB", 
                        "Color: Stainless Steel, Capacity: 20 cu ft", "Color: White, Capacity: 18 cu ft", 
                        "Type: Front Load, Capacity: 4.5 cu ft", "Type: Top Load, Capacity: 5.0 cu ft", 
                        "Color: Blue, Size: S", "Color: Red, Size: M", "Color: Green, Size: L", 
                        "Color: Dark Blue, Size: 32", 
                        "Format: Hardcover, Language: English", "Format: Paperback, Language: Spanish", 
                        "Format: eBook, Language: English", "Format: Paperback, Language: French", 
                        "Size: Size 7, Color: Orange", "Material: Graphite, Color: Black")
)
```


```{r}
library(jsonlite)
```

```{r}
json_data <- toJSON(data, pretty = TRUE)
write(json_data, file = "json_data.json")

# Save the json document to a file
print(json_data)
```
#JSON- * 1.Pros: Easy to read, and use. JSON support most of the modern programming languages.More compact than XML.
       * 2. Cons: Not optimized for large data, not as efficient when handling large datasets. 


```{r First soultion}
library(knitr)
html_data <- kable(data, format = "html")

# Save the html document to a file
write(html_data, file = "html_data.html")

html_data
```
#HTML- * 1. Pros: Like JOSON, HTML is easy to read too. Can be interactive with CSS / JavaScript. Designed can be use to displayed in the web browsers.
       * 2. Cons: HTML don't have complex data type, and not efficient for data storage(not for big data)
       
       

```{r Second soultion}
library("xtable")
html_data <- data
print(xtable(html_data), type="html", file="example.html")
```

```{r}
library(xml2)

# Create a root node
xml_root <- xml_new_root("inventory")

# Loop through the data frame and create child nodes for each row
for (i in 1:nrow(data)) {

  item_node <- xml_add_child(xml_root, "item")
  
  xml_add_child(item_node, "Category", data$Category[i])
  xml_add_child(item_node, "Item_Name", data$Item_Name[i])
  xml_add_child(item_node, "Item_ID", as.character(data$Item_ID[i]))
  xml_add_child(item_node, "Brand", data$Brand[i])
  xml_add_child(item_node, "Price", as.character(data$Price[i]))
  xml_add_child(item_node, "Variation_ID", data$Variation_ID[i])
  xml_add_child(item_node, "Variation_Details", data$Variation_Details[i])
}

# Save the XML document to a file
write_xml(xml_root, file = "inventory_data_fixed.xml")

print(xml_root)
```

#XML- * 1. Pros: XML fellows a strict structure, each element has a clear meaning.
      * 2. Cons: Large file size, and slow parsing. Not for big data.
       


```{r}
library(arrow)

write_parquet(data, "inventory_data.parquet")

# To read the data back into R
parquet_data <- read_parquet("inventory_data.parquet")

print(parquet_data)
```
#Parquet - * 1. Pros: Good for big data procressing. Fast read time.
           * 2. Cons: Parquet may be overhead for small datasets, and its more complex, may require additional learning for a new user.
